\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{ragged2e} % For \flushleft

% Set page margins
\geometry{left=1in,right=1in,top=1in,bottom=1in}

% Hide page numbers
\pagestyle{empty}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=blue,
    citecolor=blue
}

\begin{document}

% Sender's Contact Information
\begin{flushleft}
Mohamed Aziz Werghi \\
Tunis, Ben Arous \\
29836507 \\
\href{mailto:werghia.1@gmail.com}{werghia.1@gmail.com} \\
\href{https://linkedin.com/in/azizwerghi}{LinkedIn}
\end{flushleft}

\vfill % Pushes the following content down to create space

% Date
\today

\vspace{12pt} % Space between date and recipient info

% Recipient's Contact Information
\begin{flushleft}
Dear Hiring Team, \\ % Using "Hiring Team" as specific name is not provided
[Hiring Manager Title] \\
[Company Name] \\
[Company Address]
\end{flushleft}

\vspace{12pt} % Space between recipient info and salutation

\section*{Subject: Application for Data Scientist Position}
\vspace{-12pt} % Adjust spacing after section title

% Professional Salutation
Dear Hiring Team,

% Opening Paragraph
I am writing to express my enthusiastic interest in the Data Scientist position, as advertised on [Source of Advertisement]. With a strong foundation in machine learning and Python, I am confident that my skills and experience align perfectly with the requirements of this role at [Company Name].

% Body Paragraph 2 (Skills & Experience)
During my tenure as a Junior Data Scientist at DataCorp, I gained hands-on experience in developing and deploying machine learning models, specifically focusing on customer segmentation and churn prediction. My expertise in Python, coupled with my proficiency in machine learning frameworks, has allowed me to translate complex data into actionable insights. I am also adept at working with SQL for data manipulation and analysis.

% Body Paragraph 3 (Quantifiable Achievements & Impact)
One notable achievement includes successfully leading the development of a robust customer churn prediction model. This project, which leveraged Python, Pandas, and scikit-learn, aimed to identify at-risk customers, providing crucial insights for proactive retention strategies. My work directly contributed to enhancing data-driven decision-making processes and improving business outcomes.

% Body Paragraph 4 (Company Fit & Enthusiasm)
I am particularly drawn to [Company Name] because of [Specific reasons for your interest in the company]. Your [mention something specific, e.g., innovative approach, industry leadership, commitment to data-driven solutions] resonates strongly with my professional aspirations. I am eager to apply my analytical capabilities and problem-solving skills to contribute to your team's success and further develop cutting-edge data solutions.

% Closing Paragraph (Call to Action)
Thank you for considering my application. I have attached my resume for your review and welcome the opportunity to discuss how my qualifications can benefit [Company Name] in more detail. I look forward to hearing from you soon.

% Professional Closing
Sincerely,

% Signature
Mohamed Aziz Werghi

\end{document}