\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[letterpaper, margin=0.75in]{geometry} % Smaller margins for more content
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{ragged2e}
\usepackage{fontawesome5} % For modern icons

% --- COLORS ---
\definecolor{primary}{HTML}{0056B3} % A professional blue
\definecolor{darkgray}{HTML}{333333}
\definecolor{lightgray}{HTML}{666666}

% --- FONT CONFIGURATION (Optional, but good for consistency) ---
% \usepackage{roboto} % For Roboto font, often used in modern designs. Requires fontspec and XeLaTeX/LuaLaTeX.
% For pdflatex, stick to default or use Latin Modern which is good.
% If using fontspec for custom fonts, swap documentclass to 'scrartcl' or 'article' and compile with XeLaTeX/LuaLaTeX.
% Sticking to standard for Tectonic compatibility without extra font packages.

% --- HYPERLINK SETUP ---
\hypersetup{
    colorlinks=true,
    linkcolor=primary,
    urlcolor=primary,
    citecolor=primary,
    filecolor=primary,
    pdftitle={Mohamed aziz werghi - Data Scientist CV},
    pdfauthor={Mohamed aziz werghi}
}

% --- SECTION STYLING ---
\titleformat{\section}
  {\vspace{-4pt}\normalfont\Large\textbf{\color{darkgray}}}
  {}{0em}
  {\hrule\vspace{4pt}}[\vspace{4pt}\hrule]

\titlespacing{\section}{0pt}{8pt}{4pt} % Adjust spacing around sections

% --- LIST STYLING ---
\setlist[itemize]{
    itemsep=2pt, % Space between items
    parsep=0pt,  % Space between paragraphs in an item
    partopsep=0pt, % Space before the first item if list follows a paragraph
    topsep=4pt,  % Space above the list
    leftmargin=1.5em % Indent bullets
}

% --- COMMANDS ---
\newcommand{\hrfill}{\vspace{2pt}\hrulefill\vspace{2pt}} % Horizontal rule for sections

\begin{document}
\RaggedRight % Aligns text to the left margin, ragged right

% ==============================================================================
% CONTACT INFORMATION
% ==============================================================================
\begin{center}
    \vspace{-15pt} % Reduce space at the top of the document
    \color{darkgray}
    \textbf{\Huge Mohamed aziz werghi}
    \vspace{2pt}

    \small
    \href{mailto:werghia.1@gmail.com}{\faEnvelope\ werghia.1@gmail.com} \quad $|$ \quad
    \faPhone\ 29836507 \quad $|$ \quad
    \faMapMarkerAlt\ Tunis, Ben Arous \quad $|$ \quad
    \href{https://gemini.google.com/app/3fa3e864002f45d4}{\faLinkedin\ LinkedIn} \quad $|$ \quad
    \href{https://gemini.google.com/app/3fa3e864002f45d4}{\faGithub\ GitHub} \quad $|$ \quad
    \href{https://gemini.google.com/app/3fa3e864002f45d4}{\faGlobe\ Portfolio}
\end{center}
\vspace{-8pt} % Reduce space after contact info

% ==============================================================================
% SUMMARY
% ==============================================================================
\section*{Summary}
\vspace{-4pt}
\small
Highly motivated and analytical Data Scientist with a strong foundation in machine learning, statistical modeling, and data visualization. Proven ability to translate complex data into actionable insights, optimize business processes, and drive data-driven decision-making. Seeking to leverage expertise in predictive analytics and large-scale data processing to contribute to innovative projects and solve challenging real-world problems.

% ==============================================================================
% SKILLS
% ==============================================================================
\section*{Skills}
\vspace{-4pt}
\small
\textbf{Programming:} Python, R, SQL, Scala \\
\textbf{Machine Learning:} Supervised/Unsupervised Learning, Deep Learning, NLP, Time Series Analysis, Scikit-learn, TensorFlow, Keras, PyTorch \\
\textbf{Data Analysis \& Visualization:} Pandas, NumPy, Matplotlib, Seaborn, Plotly, Tableau, Power BI \\
\textbf{Big Data Technologies:} Apache Spark, Hadoop, AWS (S3, EC2, SageMaker), Google Cloud Platform (BigQuery, AI Platform) \\
\textbf{Databases:} PostgreSQL, MySQL, MongoDB, Cassandra \\
\textbf{Tools \& Other:} Git, Docker, Jupyter Notebooks, Agile Methodologies

% ==============================================================================
% WORK EXPERIENCE
% ==============================================================================
\section*{Work Experience}
\vspace{-4pt}

\textbf{Senior Data Scientist} \hfill \textbf{Jan 2021 – Present} \\
Tech Solutions Inc., New York, NY
\begin{itemize}
    \item Developed and deployed machine learning models, improving prediction accuracy by 15\% and reducing operational costs by 10\%.
    \item Designed and implemented A/B tests to optimize user engagement, leading to a 20\% increase in conversion rates.
    \item Built scalable data pipelines using Apache Spark and AWS, processing over 1TB of data daily.
    \item Collaborated with cross-functional teams to define KPIs and deliver data-driven insights that informed product strategy.
    \item Mentored junior data scientists on best practices in model development and deployment.
\end{itemize}

\vspace{6pt}

\textbf{Data Scientist} \hfill \textbf{Aug 2018 – Dec 2020} \\
FinTech Innovations, Boston, MA
\begin{itemize}
    \item Analyzed large datasets to identify trends and patterns, contributing to a 5\% improvement in fraud detection rates.
    \item Developed predictive models for customer churn, resulting in targeted retention strategies and a 7\% reduction in churn.
    \item Automated data extraction and reporting processes, saving 10+ hours per week for the analytics team.
    \item Presented complex analytical findings to stakeholders, translating technical details into clear business recommendations.
\end{itemize}

% ==============================================================================
% EDUCATION
% ==============================================================================
\section*{Education}
\vspace{-4pt}

\textbf{Master of Science in Data Science} \hfill \textbf{2017} \\
University of Data Excellence, City, State
\begin{itemize}
    \item Thesis: "Predictive Modeling for Dynamic Resource Allocation in Cloud Environments"
    \item Relevant Coursework: Advanced Machine Learning, Big Data Analytics, Statistical Inference, Natural Language Processing
\end{itemize}

\vspace{6pt}

\textbf{Bachelor of Science in Computer Science} \hfill \textbf{2015} \\
National University of Technology, City, State
\begin{itemize}
    \item Minors: Mathematics, Statistics
    \item Graduated with Honors
\end{itemize}

% ==============================================================================
% END DOCUMENT
% ==============================================================================
\end{document}