\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{ragged2e}

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=blue
}

\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=*}

\titleformat{\section}{\large\bfseries}{}{0em}{}
\titlespacing*{\section}{0pt}{1.5ex plus .2ex minus .2ex}{0.8ex plus .2ex}

\begin{document}
\raggedright

% Contact Information
{\LARGE \textbf{Moahmed Aziz Werghi}}\\[6pt]
\href{mailto:werghia.1@gmail.com}{werghia.1@gmail.com} \textbullet\ +216~29836507 \textbullet\ Tunis, Ben Arous, Mohamedia\\
\href{https://www.linkedin.com/in/mohamed-aziz-ouerghi/}{linkedin.com/in/mohamed-aziz-ouerghi} \textbullet\ 
\href{https://github.com/ouerghi0x/}{github.com/ouerghi0x}\\[12pt]

% Summary
\section*{Summary}
Motivated Software Engineer currently pursuing a Cycle d'Ingénieur in Telecommunications with hands-on internship experience. Proven ability to develop scalable applications, implement real-time monitoring solutions, and integrate advanced assistant agents. Skilled in Python and TypeScript with a strong foundation in modern development frameworks and methodologies.

% Skills
\section*{Skills}
\textbf{Programming Languages:} Python (Advanced), Typescript / Javascript (Advanced)\\
\textbf{Frameworks \& Technologies:} Spring Boot, .Net, NestJS, FastAPI, Flask (Intermediate)\\
\textbf{Project Management:} Intermediate

% Experience
\section*{Work Experience}

\textbf{Software Engineer Intern PFE} \hfill Feb 2025 -- Jul 2025\\
Bry Technology\\
\begin{itemize}
    \item Developed a Retrieval-Augmented Generation (RAG) agent and integrated it into a marketplace web application, enhancing user interaction as an intelligent assistant.
    \item Delivered a scalable solution improving customer experience and streamlining marketplace operations.
\end{itemize}

\textbf{Software Engineer Intern} \hfill Jul 2024 -- Sep 2024\\
Bry Technology\\
\begin{itemize}
    \item Built a real-time PostgreSQL monitoring system with a dynamic dashboard, incorporating anomaly detection models and Kafka for streaming data.
    \item Increased system reliability by promptly detecting and alerting database anomalies, reducing downtime risk.
\end{itemize}

% Education
\section*{Education}

\textbf{Cycle d'Ingénieur de Télécommunication} \hfill 2022 -- 2025 (Expected)\\
Ecole Nationale d'Ingénieurs de Tunis (ENIT)

\textbf{PREPA MP} \hfill 2020 -- 2022\\
ISSAT Mahdia

\textbf{BAC MATH} \hfill 2019 -- 2020\\
Lycée Mohamedia 7, Tunis

% Projects
\section*{Projects}

\textbf{Smart Classroom} \hfill Feb 2024 -- Jun 2024\\
\textit{Technologies: React, Spring Boot, C++}\\
\begin{itemize}
    \item Designed an academic administration platform featuring a dashboard to monitor teacher attendance and presence.
    \item Implemented automated energy management by controlling electricity consumption and device activity in classrooms, improving efficiency.
\end{itemize}

\textbf{Random Chat} \hfill Sep 2024 -- Nov 2024\\
\textit{Technologies: NestJS, Next.js, Prisma, Python}\\
\begin{itemize}
    \item Developed a platform enabling users to connect randomly and build friendships, focusing on real-time communication and user engagement.
\end{itemize}

% Certifications
\section*{Certifications}
\textbf{C Programming} \hfill Jan 2023 -- May 2025 (Valid)\\
Coursera

% Languages
\section*{Languages}
English --- Fluent \\
French --- Basic

\end{document}