\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{tabularx}
\usepackage{xcolor}

\definecolor{accentcolor}{HTML}{0077CC} % Example accent color

\newcommand{\cvsection}[1]{\section*{\textbf{#1}}}
\newcommand{\cvsubsection}[1]{\subsection*{\textbf{#1}}}

\begin{document}

\begin{center}
    {\Large \textbf{Sarah Johnson}} \\
    \href{mailto:sarah.johnson@example.com}{sarah.johnson@example.com} \hspace{1cm} +1 (555) 123-4567 \hspace{1cm} 123 Elm Street, San Francisco, CA \\
    \href{https://linkedin.com/in/sarahjohnson}{\faLinkedin} \hspace{1cm} \href{https://github.com/sjohnson-dev}{\faGithub} \hspace{1cm} \href{https://sarahjohnson.dev}{\faGlobe}
\end{center}

\cvsection{Summary}
Highly motivated and results-oriented Software Engineer with expertise in frontend development using modern JavaScript frameworks. Proven ability to develop scalable and performant web applications.  Seeking a challenging role where I can leverage my skills and experience to contribute to a dynamic team.

\cvsection{Skills}
\begin{tabularx}{\textwidth}{lX}
    \textbf{Expert} & JavaScript \\
    \textbf{Advanced} & React, Node.js \\
    \textbf{Intermediate} & Python, Docker \\
\end{tabularx}

\cvsection{Experience}
\cvsubsection{Google \hfill June 2022 -- Present}
\textbf{Frontend Engineer} \\
\begin{itemize}
    \item Developed scalable UI components using React.
    \item Improved page load speed by 30\%.
\end{itemize}

\cvsubsection{Facebook \hfill June 2021 -- Sept 2021}
\textbf{Software Engineering Intern} \\
\begin{itemize}
    \item Built internal tools for performance tracking in React and TypeScript.
\end{itemize}


\cvsection{Education}
\cvsubsection{Master of Science in Artificial Intelligence \hfill MIT \hfill 2020 -- 2022}
\cvsubsection{Bachelor of Science in Computer Science \hfill Stanford University \hfill 2015 -- 2019}

\cvsection{Projects}
\begin{tabularx}{\textwidth}{lX}
    \textbf{DevConnect} & \href{https://devconnect.app}{https://devconnect.app} \hfill (Jan 2023 -- June 2023) \\
    & A professional networking platform for developers.  Next.js, MongoDB, Tailwind CSS. \\
    \textbf{AI Resume Builder} & \href{https://resumebuilder.ai}{https://resumebuilder.ai} \hfill (July 2023 -- Oct 2023) \\
    & Generates optimized resumes using OpenAI APIs. React, OpenAI API, Express.js. \\
\end{tabularx}


\cvsection{Certifications}
\begin{itemize}
    \item AWS Certified Developer – Associate \hfill Amazon Web Services \hfill March 2022
    \item Certified Kubernetes Application Developer (CKAD) \hfill Linux Foundation \hfill August 2023
\end{itemize}

\cvsection{Languages}
\begin{itemize}
    \item English (Native)
    \item Spanish (Professional)
    \item French (Intermediate)
\end{itemize}

\end{document}
