\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{letterpaper, margin=1in} % Set appropriate page margins
\usepackage{hyperref} % For clickable links (email, LinkedIn)
\usepackage{xcolor} % For colors, though not strictly needed for this
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
}

\begin{document}

% Sender's Contact Information
\begin{flushleft}
Mohamed Aziz Werghi \\
Tunis, Ben Arous \\
29836507 \\
\href{mailto:werghia.1@gmail.com}{werghia.1@gmail.com} \\
\href{https://linkedin.com/in/azizwerghi}{LinkedIn}
\end{flushleft}

\vspace{1em} % Add some vertical space

% Date
\today

\vspace{1em} % Add some vertical space

% Recipient's Contact Information
\begin{flushleft}
Dear Hiring Team, \\
[Hiring Manager Title] \\
[Company Name] \\
[Company Address]
\end{flushleft}

\vspace{1em} % Add some vertical space

% Salutation
Dear Hiring Team,

\vspace{1em} % Add some vertical space

% Opening Paragraph
I am writing to express my enthusiastic interest in the Data Scientist position, which I discovered through [Source of Advertisement]. With a solid foundation in machine learning and Python, coupled with practical experience in developing data-driven solutions, I am confident that my skills and passion align perfectly with the requirements of this role at [Company Name].

\vspace{1em} % Add some vertical space

% Body Paragraph 2 (Skills & Experience)
During my tenure as a Junior Data Scientist at DataCorp, I gained valuable hands-on experience in building robust machine learning models. My responsibilities included developing solutions for critical business needs such as customer segmentation and churn prediction. This experience has honed my proficiency in leveraging Python and its extensive libraries to tackle complex data challenges, transforming raw data into actionable insights.

\vspace{1em} % Add some vertical space

% Body Paragraph 3 (Quantifiable Achievements & Impact)
A notable achievement includes the successful development of a customer churn prediction model, utilizing Python, Pandas, and scikit-learn. This project demonstrated my ability to apply advanced analytical techniques to identify at-risk customers, providing businesses with the foresight to implement proactive retention strategies. My commitment to delivering data-driven solutions is evidenced by my strong analytical skills and my capacity to translate complex data into clear, impactful results.

\vspace{1em} % Add some vertical space

% Body Paragraph 4 (Company Fit & Enthusiasm)
I am particularly drawn to [Company Name] due to [Specific reasons for your interest in [Company Name]]. Your commitment to [mention a specific company value, recent project, or industry leadership] resonates with my own professional aspirations. I am eager to contribute my expertise in machine learning and data analysis to a forward-thinking organization like yours, where I can continue to innovate and make a tangible impact.

\vspace{1em} % Add some vertical space

% Closing Paragraph (Call to Action)
Thank you for considering my application. I am very eager to discuss how my qualifications and experiences can benefit [Company Name] and contribute to your team's success. My resume is attached for your review, and I am available for an interview at your earliest convenience.

\vspace{1em} % Add some vertical space

% Professional Closing
Sincerely,

\vspace{2em} % Space for signature

% Signature
Mohamed Aziz Werghi

\end{document}