\documentclass[10pt, letterpaper]{article} % Use article class for simplicity, 10pt font, letterpaper size
\usepackage[utf8]{inputenc} % For international characters
\usepackage[T1]{fontenc} % For proper font encoding

% Geometry for page margins: Defines margins for the document.
\usepackage[margin=0.8in, top=0.6in, bottom=0.6in]{geometry}

% Hyperlinks: For email, LinkedIn, GitHub, and portfolio links.
% 'colorlinks=true' makes the links colored instead of boxed.
% 'urlcolor' and 'linkcolor' set the color of URLs and internal links.
\usepackage[colorlinks=true, urlcolor=primarycolor, linkcolor=primarycolor]{hyperref}

% Lists for compact spacing: 'enumitem' provides control over list environments.
% 'noitemsep', 'topsep', 'partopsep', 'parsep' remove extra vertical space between items and paragraphs.
% 'leftmargin=*' sets the left margin of the list to match the text margin.
\usepackage{enumitem}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt}

% Colors: Defines a custom color for headings and links.
\usepackage{xcolor}
\definecolor{primarycolor}{RGB}{23, 114, 187} % A professional blue shade

% Font: Using CM Bright for a clean, sans-serif look. Widely available.
\usepackage{cmbright} 

% Section formatting: 'titlesec' allows customization of section titles.
% 'titlespacing*' sets the spacing around sections (left, before-skip, after-skip).
% 'titleformat' defines the appearance of the section title (font, color, alignment).
% '[\titlerule]' adds a horizontal rule after each section title.
\usepackage{titlesec}
\titlespacing*{\section}{0pt}{1.5em}{0.8em}
\titleformat{\section}
  {\normalfont\large\bfseries\color{primarycolor}}{}{0em}{\MakeUppercase}
  [\titlerule]

% Ragged Right alignment: Prevents full justification, often preferred for CVs for better readability.
\usepackage{ragged2e}
\RaggedRight

% Font Awesome icons: For professional icons in the contact information.
\usepackage{fontawesome5} 

% Remove page numbers: CVs typically don't have page numbers.
\pagestyle{empty}

\begin{document}

% --- CONTACT INFORMATION ---
\begin{center}
    \vspace{-1em} % Adjust vertical space before name
    {\Huge\textbf{Mohamed Aziz Werghi}} \\ % Name of the applicant
    \vspace{0.2em} % Small vertical space between name and contact details
    \begin{itemize}[itemsep=0em, parsep=0em, topsep=0em, leftmargin=0pt, labelsep=0.5em, itemindent=0pt]
        \item[\faEnvelope] \href{mailto:werghia.1@gmail.com}{werghia.1@gmail.com}
        \item[\faPhone] +216 29836507
        \item[\faMapMarkerAlt] Tunis, Ben Arous
        \item[\faLinkedin] \href{https://gemini.google.com/app/3fa3e864002f45d4}{linkedin.com/in/mohamedazizwerghi} % Replace with actual LinkedIn URL
        \item[\faGithub] \href{https://gemini.google.com/app/3fa3e864002f45d4}{github.com/mohamedazizwerghi} % Replace with actual GitHub URL
        \item[\faGlobe] \href{https://gemini.google.com/app/3fa3e864002f45d4}{portfolio.com/mohamedazizwerghi} % Replace with actual Portfolio URL
    \end{itemize}
    \vspace{-0.5em} % Adjust vertical space after contact information
\end{center}

% --- SUMMARY/OBJECTIVE ---
\section*{Summary}
\noindent Highly motivated and results-driven Data Scientist with a strong foundation in statistical analysis, machine learning, and data visualization. Proven ability to translate complex data into actionable insights, develop predictive models, and optimize business processes. Eager to leverage analytical skills and technical expertise to contribute to innovative projects and drive data-informed decision-making in a dynamic environment.

% --- SKILLS ---
\section*{Skills}
\begin{itemize}
    \item \textbf{Programming Languages:} Python (Pandas, NumPy, Scikit-learn, Matplotlib, Seaborn), R, SQL
    \item \textbf{Machine Learning:} Regression, Classification, Clustering, Time Series Analysis, Natural Language Processing (NLP), Deep Learning (TensorFlow, Keras)
    \item \textbf{Data Visualization:} Tableau, Power BI, Matplotlib, Seaborn, Plotly
    \item \textbf{Big Data Technologies:} Apache Spark, Hadoop, AWS S3, Redshift
    \item \textbf{Tools \& Platforms:} Git, Docker, Jupyter Notebook, Google Cloud Platform (GCP), Azure, Databricks
    \item \textbf{Methodologies:} A/B Testing, Statistical Modeling, Predictive Analytics, Feature Engineering, Model Deployment
\end{itemize}

% --- WORK EXPERIENCE ---
\section*{Work Experience}

\textbf{Junior Data Scientist} \hfill \textit{Jan 2023 -- Present} \\
\textit{InnovateTech Solutions} \hfill \textit{Tunis, Tunisia}
\begin{itemize}
    \item Developed and deployed machine learning models to predict customer churn, leading to a 15\% reduction in customer attrition within 6 months.
    \item Performed extensive data cleaning, transformation, and feature engineering on large datasets using Python (Pandas, NumPy) to prepare data for model training.
    \item Collaborated with cross-functional teams to define business problems, gather requirements, and present data-driven solutions to stakeholders.
    \item Created interactive dashboards using Tableau to visualize key performance indicators, improving data accessibility and decision-making for management.
    \item Optimized existing SQL queries, reducing data retrieval times by 30\% for critical business reports.
\end{itemize}

\textbf{Data Analysis Intern} \hfill \textit{Jul 2022 -- Dec 2022} \\
\textit{Global Data Insights} \hfill \textit{Online}
\begin{itemize}
    \item Assisted senior data scientists in analyzing customer behavior data, contributing to insights that improved marketing campaign effectiveness by 10\%.
    \item Conducted exploratory data analysis (EDA) on various datasets to identify trends, outliers, and patterns using statistical methods and visualization tools.
    \item Prepared detailed reports and presentations summarizing analytical findings for internal team meetings.
    \item Participated in the development of a recommendation system prototype, contributing to data collection and pre-processing tasks.
\end{itemize}

% --- EDUCATION ---
\section*{Education}

\textbf{Master of Science in Data Science} \hfill \textit{Sep 2021 -- Jun 2023} \\
\textit{University of Data Science \& AI} \hfill \textit{Tunis, Tunisia}
\begin{itemize}
    \item Specialization in Advanced Machine Learning and Big Data Analytics.
    \item \textbf{Relevant Coursework:} Deep Learning, Natural Language Processing, Statistical Inference, Cloud Computing for Data Science.
    \item \textbf{Master's Thesis:} "Predictive Modeling for Financial Market Volatility using LSTM Networks."
\end{itemize}

\textbf{Bachelor of Science in Computer Science} \hfill \textit{Sep 2018 -- Jun 2021} \\
\textit{National Institute of Applied Sciences} \hfill \textit{Tunis, Tunisia}
\begin{itemize}
    \item Graduated with Honors.
    \item \textbf{Key Courses:} Data Structures \& Algorithms, Database Management Systems, Probability \& Statistics, Artificial Intelligence.
\end{itemize}

\end{document}